Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-18 ICML2019/main.tex
clear up the formulas in accuracy section and fix macros file
Shrink

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.

	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.

  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.

	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
\end{itemize}

\section{Preliminaries}
\label{sec_background}
\noindent \textbf{Bayesian inference.} 
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is defined as:
\[
  \Pr(\theta | \dataobs) \equiv \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression $\Pr(\dataobs | \theta)$ denotes the
\emph{likelihood} of observing $\dataobs$ under a value of
$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distribution of the prior. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior
simplifies calculations and allows for inference to be performed in a
recursive fashion over the data.
% Then, we have:
% \[
%   \bysinfer(\Pr(\dataobs | \theta), \Pr(\theta), \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
% \]
% \noindent \textbf{Beta-binomial System.}
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
We will consider the situation where the underlying data is drawn from a binomial distribution
($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
the parameter --informally called \emph{bias}-- of a Bernoulli
distributed random variable and $n$ is the number of draws. The
prior distribution over $\theta\in [0,1]$ is going to be a beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.
The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
in section \ref{} when the private mechanisms will be described.
% \noindent \textbf{Dirichlet-multinomial Systems.}

The beta-binomial model can be immediately generalized to the Dirichlet-multinomial model, with underlying data multinomially distributed.
The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichlet distribution, $\dirichlet{\valpha}$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
   \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)=\dirichlet{\valpha + \Delta \valpha} 
\]
where $+$ denotes the componentwise sum of vectors of reals.

@@

A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ and codomain $\range$, is $\epsilon$-differential private, if for all adjacent
\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, iff
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
\begin{equation*}
\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] \leq e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
\end{equation*}

@@

\noindent \textbf{Technical Problem Statement.}
\label{subsec_problem}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.\\
However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
\todo{However, distance between
distributions are more naturally to be measured by distribution
metrics such as $f$-divergence, Hellinger distance, etc., than the $\ell_1$ norm shown above.}
{\color{blue} changed a bit, still not sure this is a good way to put it...}
This gives us motivation for exploring the design space
of mechanisms by considering different norms. e.g. a norm over space of measures.
to compute the sensitivity and provide guarantees on the accuracy.\\
We will use the Hellinger distance $\hellinger(\cdot,\cdot)$, 
Given two probability distributions $\textup{P}$ and $\textup{Q}$,
the Hellinger distance between them is defined as:
\[
\hellinger^2(P,Q) = \frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
\]
When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above reduces to: 
\[
 \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
  \item It simplifies calculations in the case of the probabilistic models considered here.

@@

  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity},
    taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{{The local sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$. This is just an attempt since local sensitivity is non-private. $\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\[
\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

@@

\begin{thm}
\label{thm_gamma_smooth}
Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:\\
For any $\adj{\dataobs}{\dataobs'}$:
\begin{equation}
\label{eq_gamma_smooth}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation}

\end{thm}
Proof is in Appendix I.

@@

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.19673467014,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\ 
&= 0.11932560927,\\
&\lapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} \\
&= 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}\\
&= 0.31606027941,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} }\\
&= 0.11627207896,\\
&\ilapmechPr{\dataobs}{\textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}\\
&= 0.04277410743.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$

  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

>>>>

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
\end{itemize}

\section{Preliminaries}
\label{sec_background}
\noindent \textbf{Bayesian inference.} 
Given a prior belief $\Pr(\theta)$ on some parameter $\theta$,
and an observation $\dataobs$, the posterior distribution on $\theta$ given $\dataobs$ is defined as:
\[
  \Pr(\theta | \dataobs) \equiv \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
\]
where the expression $\Pr(\dataobs | \theta)$ denotes the
\emph{likelihood} of observing $\dataobs$ under a value of
$\theta$. Since we consider $\dataobs$ to be fixed, the likelihood is
a function of $\theta$.
For the same reason $\Pr(\dataobs)$ is a constant independent of $\theta$.
Usually in statistics the prior distribution $\Pr(\theta)$ is chosen so that it represents
the initial belief on $\theta$, that is, when no data has been observed. In practice though,
prior distributions and likelihood functions are usually chosen so that the posterior
belongs to the same \emph{family} of distribution of the prior. In this case we say that the prior
is conjugate to the likelihood function. Use of a conjugate prior
simplifies calculations and allows for inference to be performed in a
recursive fashion over the data.
% Then, we have:
% \[
%   \bysinfer(\Pr(\dataobs | \theta), \Pr(\theta), \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}
% \]
% \noindent \textbf{Beta-binomial System.}
In this work we will consider a specific instance of Bayesian inference and one of its generalizations.
We will consider the situation where the underlying data is drawn from a binomial distribution
($\thicksim \binomial{n}{\theta}$), where $\theta$ represents
the parameter --informally called \emph{bias}-- of a Bernoulli
distributed random variable and $n$ is the number of draws. The
prior distribution over $\theta\in [0,1]$ is going to be a beta
distribution, $\betad(\alpha, \beta)$, with parameters
$\alpha,\beta\in\mathbb{R}^{+}$, and with p.d.f:
\[
  \Pr(\theta)\equiv \frac{\theta^{\alpha} (1- \theta)^{\beta}}{\betaf(\alpha,\beta)}
\]
where $\betaf(\cdot,\cdot)$ is the beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ binary values, that is $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, and the likelihood function is:
\[
  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}
\]
where $\Delta \alpha = \sum_{i=1}^{n}x_i$.
The posterior distribution over $\theta$ can be easily proven to be equal to:\[\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\]
From now on we will denote by $\bysinfer(\binomial{n}{\theta}, \betad(\alpha, \beta), \dataobs)$ the previous
posterior distribution. This notation will prove itself handy when its arguments will change types in the next example and
in section \ref{} when the private mechanisms will be described.
% \noindent \textbf{Dirichlet-multinomial Systems.}

The beta-binomial model can be immediately generalized to the Dirichlet-multinomial model, with underlying data multinomially distributed.
The \emph{bias} is represented by the parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichlet distribution, $\dirichlet{\valpha}$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
\Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
\Pr(\dataobs|\vtheta)\equiv\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
   \bysinfer(\multinomial{n}{\vtheta}, \dirichlet{\valpha}, \dataobs)=\dirichlet{\valpha + \Delta \valpha} 
\]
where $+$ denotes the componentwise sum of vectors.

@@

A randomized mechanism $\mathcal{M}$ with domain $\mathbb{N}^{|\mathcal{X}|}$ and codomain $\range$, is $\epsilon$-differential private, if for all adjacent
\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^n$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, iff
$\sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } $\dataobs, \dataobs' \in \mathbb{N}^{|\mathcal{X}|}$ and all $\mathcal{S} \subseteq \range$:
\begin{equation*}
\Pr[\mathcal{M}(\dataobs) \in \mathcal{S}] \leq e^\epsilon \Pr[\mathcal{M}(\dataobs') \in \mathcal{S}].
\end{equation*}

@@

\noindent \textbf{Technical Problem Statement.}
\label{subsec_problem}
We are interested in exploring mechanisms for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (Beta, Dirichlet distribution) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{sec_mechs}.\\
However, in previous works, the accuracy of the posterior was measured with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above.
\todo{However, distance between
distributions are more naturally to be measured by distribution
metrics such as $f$-divergence, Hellinger distance, etc., than the $\ell_1$ norm shown above.}
{\color{blue} changed a bit, still not sure this is a good way to put it...}
This gives us motivation for exploring the design space
of mechanisms by considering different norms. e.g. a norm over space of measures.
to compute the sensitivity and provide guarantees on the accuracy.\\
We will use the Hellinger distance $\hellinger(\cdot,\cdot)$, 
Given two probability distributions $\textup{P}$ and $\textup{Q}$,
the Hellinger distance between them is defined as:
\[
\hellinger^2(P,Q) = \frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
\]
When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$ the above reduces to: 
\[
 \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
  \item It simplifies calculations in the case of the probabilistic models considered here.

@@

  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity},
    taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying an upper bound on local sensitivity instead of using global sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{{The local sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$. This is just an attempt since local sensitivity is non-private. $\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\[
\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
\begin{equation}\label{eq:local_sensitivity_scoring}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation}

@@

\begin{thm}
\label{thm_gamma_smooth}
Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
whenever $\adj{\dataobs}{\dataobs'}$, 
%\begin{equation}
%\label{eq_gamma_smooth}
$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
%\end{equation}
\end{thm}
(Proof is in Appendix I.)

@@

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
} = 0.19673467014,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
\end{aligned}
  } = 0.11932560927,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
  \end{aligned}
} = 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
  \end{aligned}
} = 0.116272079,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
    \end{aligned}
} = 0.04277411.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}
